\cvsection{Projects}
\begin{cventries}
	\cventry
	{An open source dashboard application to coordinate ics links from Airbnb and VRBO to create an all-in-one calendar for easier property management. This project is built with Ruby on Rails as the backend and with React and Redux for the frontend. The entire frontend is built as a single page application. During the course of this project I kept an open line of communication with the client in order to deliver the exact features they needed in the most timely manner possible.}
	{Bnbwithme Dashboard}
	{react, redux, ruby on rails, javascript, webpacker}
	{https://github.com/greasysock/bnbwithme-dashboard}
	{}
	
	\vspace{-5mm}
	\cventry
	{Created with ruby on rails. My portfolio site features an interactive blog and comments section driven by JavaScript and ActionCable provided by Ruby on Rails. It also includes a fully functional admin view for controlling content on the site.}
	{Portfolio Site}
	{ruby, ruby on rails, ActionCable, javascript, bootstrap, postgresql, git}
	{https://www.chrismedia.dev}
	{}
	
	\vspace{-5mm}
	\cventry
	{A simple cron job for synchronizing ics links to the database, working in conjunction with Bnbwithme Dashboard.}
	{Bnbwithme Dashboard Calendar}
	{python, postgresql, sqlalchemy, requests}
	{https://github.com/greasysock/bnbwithme-calendar}
	{}
	
	\vspace{-5mm}
	\cventry
	{A small go library for decrypting cookies created with rails for the creation of a devise session.}
	{railscookie}
	{go, openssl}
	{https://github.com/greasysock/railscookie}
	{}

\end{cventries}